% Autor: Francisco Javier Barranco Tena
% Bibliografía
% Alt + z o Option + z para activar el word wrap en Visual Studio Code

\begin{thebibliography}{99}
    
    \bibitem{WHO_Road_Safety}
        World Health Organization (WHO), 2018. Global Status Report on Road Safety 2018. Geneva, Switzerland: The World Health Organization (WHO). Available at: \url{https://www.who.int/publications/i/item/9789241565684}

    \bibitem{MACROECON_Road_Safety}
        Chen, S., Kuhn, M., Prettner, K. and Bloom, D.E., 2019. The global macroeconomic burden of road injuries: estimates and projections for 166 countries. Lancet Planet Health, 3(9), pp.e390–398. Available at: \url{https://www.sciencedirect.com/science/article/pii/S2542519619301706}.

    \bibitem{Pavement_Anomalies_Accelerometer}
        Bustamante-Bello, R., García-Barba, A., Arce-Saenz, L.A., Curiel-Ramirez, L.A., Izquierdo-Reyes, J. and Ramirez-Mendoza, R.A., 2022. Visualizing Street Pavement Anomalies through Fog Computing V2I Networks and Machine Learning. Sensors, 22(2), p.456. Available at: \url{https://doi.org/10.3390/s22020456}.

    \bibitem{LIDAR_Blasiis}
        De Blasiis, M.R., Di Benedetto, A. and Fiani, M., 2020. Mobile Laser Scanning Data for the Evaluation of Pavement Surface Distress. Remote Sensing, 12(6), p.942. Available at: \url{https://doi.org/10.3390/rs12060942}.

    \bibitem{LIDAR_VanDerHorst}
        van der Horst, B.B., Lindenbergh, R.C. and Puister, S.W.J., 2019. Mobile laser scan data for road surface damage detection. Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci., XLII-2/W13, pp.1141–1148. Available at: \url{https://doi.org/10.5194/isprs-archives-XLII-2-W13-1141-2019}.

    \bibitem{CRDDC2022_paper}
        Arya, D., Maeda, H., Ghosh, S., Toshniwal, D., Omata, H., Kashiyama, T. and Sekimoto, Y., 2022. Crowdsensing-based Road Damage Detection Challenge (CRDDC’2022). In: 2022 IEEE International Conference on Big Data (Big Data), pp.6378-6386. Available at: \url{https://doi.org/10.1109/BigData55660.2022.10021040}.

    \bibitem{CRDDC2022_review}
        Arya, D., Maeda, H. and Sekimoto, Y., 2024. From global challenges to local solutions: A review of cross-country collaborations and winning strategies in road damage detection. Advanced Engineering Informatics, 60, p.102388. Available at: \url{https://doi.org/10.1016/j.aei.2024.102388}.

    \bibitem{YOLO}
        Redmon, J., Divvala, S., Girshick, R. and Farhadi, A., 2016. You Only Look Once: Unified, Real-Time Object Detection. In: 2016 IEEE Conference on Computer Vision and Pattern Recognition (CVPR), pp.779–788.

    \bibitem{yolov8_ultralytics}
        Jocher, G., Chaurasia, A. and Qiu, J., 2023. Ultralytics YOLOv8. Version 8.0.0. Available at: \url{https://github.com/ultralytics/ultralytics}. ORCID: 0000-0001-5950-6979, 0000-0002-7603-6750, 0000-0003-3783-7069. License: AGPL-3.0.

    \bibitem{COCO}
        Lin, T.Y., Maire, M., Belongie, S., Hays, J., Perona, P., Ramanan, D., Dollár, P. and Zitnick, C.L., 2014. Microsoft COCO: Common Objects in Context. CoRR, abs/1405.0312. Available at: \url{http://arxiv.org/abs/1405.0312}.

    \bibitem{Roboflow100}
        Ciaglia, F., Zuppichini, F.S., Guerrie, P., McQuade, M. and Solawetz, J., 2022. Roboflow 100: A Rich, Multi-Domain Object Detection Benchmark. arXiv preprint. Available at: \url{https://arxiv.org/abs/2211.13523}.

    \bibitem{whats-new-in-yolov8}
        Solawetz, J., 2023. What is YOLOv8? The Ultimate Guide. Roboflow Blog. Available at: \url{https://blog.roboflow.com/whats-new-in-yolov8/}.

    \bibitem{yolov8-architecture-blog}
        Torres, J., 2024. YOLOv8 Architecture: A Deep Dive into its Architecture. YOLOv8.org. Available at: \url{https://yolov8.org/yolov8-architecture/}.

    \bibitem{yolov8-architecture-blog2}
        Torres, J., 2024. YOLOv8 Architecture Explained: Exploring the YOLOv8 Architecture. YOLOv8.org. Available at: \url{https://yolov8.org/yolov8-architecture-explained/}.

    \bibitem{RangeKing_GitHub}
        RangeKing, 2024. GitHub User Profile. Available at: \url{https://github.com/RangeKing}.

    \bibitem{SiameseAnchorFree}
        Zhang, J., Huang, B., Ye, Z. et al., 2021. Siamese anchor-free object tracking with multiscale spatial attentions. Sci Rep, 11, p.22908. Available at: \url{https://doi.org/10.1038/s41598-021-02095-4}.

    \bibitem{RDD2022_data_paper}
        Arya, D., Maeda, H., Ghosh, S., Toshniwal, D. and Sekimoto, Y., 2022. RDD2022: A multi-national image dataset for automatic Road Damage Detection. Available at: \url{https://www.researchgate.net/publication/363668453_RDD2022_A_multi-national_image_dataset_for_automatic_Road_Damage_Detection}.

    \bibitem{RoadDamageDetector_repo}
        RoadDamageDetector GitHub Repository, 2022. Available at: \url{https://github.com/sekilab/RoadDamageDetector}.

    \bibitem{RDD2022_dataset}
        Arya, D., Maeda, H., Sekimoto, Y., Omata, H., Ghosh, S.K., Toshniwal, D. et al., 2022. RDD2022 - The multi-national Road Damage Dataset released through CRDDC'2022. figshare. Dataset. Available at: \url{https://doi.org/10.6084/m9.figshare.21431547.v1}.

    \bibitem{RDD2022_datasetNinja}
        RDD2022 DatasetNinja, 2022. RDD2022 DatasetNinja Download Page. Available at: \url{https://datasetninja.com/road-damage-detector}.

    \bibitem{IoU_image}
        Intersection over Union (IoU) Diagram, 2023. Available at: \url{https://idiotdeveloper.com/what-is-intersection-over-union-iou/}.

    \bibitem{ultralytics_train}
        Ultralytics, 2023. Model Training with Ultralytics YOLO. Available at: \url{https://docs.ultralytics.com/modes/train}.

    \bibitem{ultralytics_yolov8_docs}
        Ultralytics, 2023. YOLOv8 Documentation. Available at: \url{https://docs.ultralytics.com/models/yolov8/}.

    \bibitem{TFG_Repository}
        Barranco Tena, F.J., 2023. Repositorio GitHub del TFG "Detección de estado de pavimento y aceras mediante Computer Vision". Available at: \url{https://github.com/JaviBT/tfg-informatica}.

    \bibitem{KFoldCV_image}
        Wikipedia, 2013. K-fold cross-validation Diagram. Available at: \url{https://es.wikipedia.org/wiki/Archivo:K-fold_cross_validation.jpg}. Licensed under Creative Commons Attribution-Share Alike 3.0 Unported (\url{https://creativecommons.org/licenses/by-sa/3.0/deed.en}).

    \bibitem{ultralytics_tasks}
        Ultralytics, 2023. Ultralytics YOLOv8 Tasks. Available at: \url{https://docs.ultralytics.com/tasks/}.

    \bibitem{ORDDC2024}
        ORDDC2024, 2024. Optimized Road Damage Detection Challenge 2024. Available at: \url{https://orddc2024.sekilab.global/}.

    \bibitem{Leaderboard_CRDDC2022}
        CRDDC2022. 2024. CRDDC2022 Leaderboard. Retrieved from \url{https://crddc2022.sekilab.global/leaderboard/}
    
    \bibitem{yolov8-arq-neck}
        YOLOv8 Architecture. 2024. Retrieved from \url{https://github.com/open-mmlab/mmyolo/blob/dev/configs/yolov8/README.md/}


        
\end{thebibliography}  